### 2024-09-24 paper/paper.qmd
Update paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction
Having operated for over 100 years, the Toronto Transit Commission (TTC) has become one of the most visible and representative public transportation organizations in North America. It is well-known as the primary mode of public transportation in Toronto's daily life. Within the TTC, the bus network typically experiences higher daily ridership compared to streetcars, while subways accommodate the largest volume of passengers due to their central role in covering longer routes. Frequent riders often notice delays that arise on a daily basis. As delays become worse and services becoming increasingly inconsistent, it is important to examine the potential causes, allowing the TTC to identify and implement effective solutions.

This paper will identify the correlations of public transit delays across different types of transportation. The data utilized for analysis, including both records and census data, measurements, is in {#sec-data}. In {#sec-results}, I will talk about the predicted results derived from the data, this includes the result of the differences in delays between buses, streetcars, and subways. Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language `R`[@citeR] . The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-09-24 paper/paper.qmd
Update paper.qmd

@@
 author: 
-  - First author
-  - Another author
+  - Dong Jun Yoon
 thanks: "Code and data are available at: LINK."

### 2024-09-24 paper/paper.qmd
Update paper.qmd

@@
 title: "My title"
-subtitle: "My subtitle if needed"
 author: 

### 2024-09-24 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "My title"
+title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
 author: 
   - Dong Jun Yoon
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/DJY1231/TTC-report-2024.git"
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper analyzes TTC delay data to understand patterns and causes of delays.
+It finds buses experience the most delays, especially on certain routes, while subways have frequent undocumented delays.
+Mechanical issues, operations, and diversions are most common delay causes.
+The analysis indicates the need to reduce bus delays through more vehicles or tactics like bus bridging on certain routes."
 format: pdf
@@
 bibliography: references.bib
----
 

### 2024-09-24 paper/paper.qmd
Update paper.qmd

@@
 title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
-author: 
-  - Dong Jun Yoon
+author: "Dong Jun Yoon"
 thanks: "Code and data are available at: https://github.com/DJY1231/TTC-report-2024.git"
@@
 # Data {#sec-data}
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
+## Data Source
+## Data Measurement
 
@@
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
 
@@
 # References
+R Core Team. 2023. R: A Language and Environment for Statistical Computing. Vienna,
+Austria: R Foundation for Statistical Computing. https://www.R-project.org/.

### 2024-09-25 paper/paper.qmd
Update paper.qmd

@@
 ## Data Source
-## Data Measurement
+The data are gathered from Open Data Toronto's report on TTC delays.
+The datasets, published by the TTC, include: the first dataset, which presents delay statistics for subways in 2024; the second dataset, which details delay statistics for buses in 2024; and the third dataset, which provides delay statistics for streetcars in 2024.
 
-Talk more about it.
+# Data Analysis
+The dataset provides information that offers insights of public transit delays across different types of transportation.
+The y-axis represents  The x-axis corresponds ,representing the total income for each year.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
+Additionally, data cleaning and analysis were conducted using the base statistical programming language R (R Core Team 2023), tidyverse (Wickham et al.
+2019), ggplot2 (Wickham 2016), dplyr (Wickham et al.
+2023), readr (Wickham, Hester, and Bryan 2023), tibble (Müller and Wickham 2023), janitor (Firke 2023), and knitr (Xie 2023) package were used.
 

### 2024-09-25 paper/paper.qmd
Update paper.qmd

@@
 # Introduction
+
 Having operated for over 100 years, the Toronto Transit Commission (TTC) has become one of the most visible and representative public transportation organizations in North America.
@@
 ## Data Source
-The data are gathered from Open Data Toronto's report on TTC delays.
-The datasets, published by the TTC, include: the first dataset, which presents delay statistics for subways in 2024; the second dataset, which details delay statistics for buses in 2024; and the third dataset, which provides delay statistics for streetcars in 2024.
+The data were gathered from Open Data Toronto's report on TTC delays.
+The datasets, published by the TTC, include the following: the first dataset presents delay statistics for subways in 2024 from January 1 to August 31; the second dataset details delay statistics for buses in 2024 from January 1 to August 31; and the third dataset provides delay statistics for streetcars in 2024 from January 1 to August 31.
 
@@
 2023), readr (Wickham, Hester, and Bryan 2023), tibble (Müller and Wickham 2023), janitor (Firke 2023), and knitr (Xie 2023) package were used.
+
+# Overview of datasets
+```{r}
+library(dplyr)
+library(knitr)
+data <- read.csv("ttc_bus_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Incident, Min.Delay, Min.Gap) %>% 
+  head(10)
+
+# Print the data with lines between columns
+kable(subset_data) 
+```
+Table 1: Sample of bus delay statistics; the first 10 rows of TTC bus delay over time: Jan 1 to Aug 31, 2024.
+
+```{r}
+library(dplyr)
+library(knitr)
+data <- read.csv("ttc_subway_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Code, Min.Delay, Min.Gap) %>% 
+  head(10)
+
+# Print the data with lines between columns
+kable(subset_data) 
+```
+Table 2: Sample of subway delay statistics; the first 10 rows of TTC subway delay over time: Jan 1 to Aug 31, 2024.
+
+Both Table 1 and Table 2 include:
+
+1. Date: The dataset shows the date when the delay occurred.
+2. Time: The dataset contains information on the time the delay occurred.
+3. Day: The dataset indicates the day of the week when the delay occurred.
+4. Incident: The dataset displays the reason for the delay, such as a general delay, emergency services, or security issues.
+5.
+Min.Delay and Min.Gap: The dataset likely represents 'Min Delay' and 'Min Gap,' both measured in minutes.
+'Min Delay' refers to the delay in the schedule for the next bus, while 'Min Gap' indicates the scheduled time, between the bus ahead and the following bus.
+
+The total bus delay dataset contains 40,447 entries, while the subway delay dataset contains 17,517 entries.
+We can indicate that delays in the bus has occurred approximately 2.35 times more than the subway delay.
+
+Both datasets went through basic cleaning for readability and irrelevant or unusable columns were removed and not considered in this report.
+Originally, the subway data reported the incident causing the delay as a unique code rather than an understandable description.
+This description was included instead in a separate table from the same package (Data 2023b).
+Using merge from dplyr (Wickham et al.
+2023), the incident was mapped to a generalized version of the description to match with the same set of generalized descriptions in the bus delay data.
+This selection into sections based on the description important to note due to the potential subjectivity of the sorting.
+There are incident descriptions in which the record may fall in one or the other.
+Please see the data cleaning scripts for more details.
+
+# Discussion
+
+Relate your analysis to the themes mentioned in Bouie (2022), discussing the importance of remembering and analyzing historical events through data.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 Please see the data cleaning scripts for more details.
+
+# Data Visualization
+```{r}
+
+```
+
+Figure 1: Distribution of Bus and Streetcar Delay Reasons
+
+Figure 1 illustrates the main reasons for bus and streetcar delays.
+The primary cause of delays for bus and streetcars are mechanical issues, followed by operational issues, security concerns, diversions, and general delays.
+Other reasons can be observed in Figure 1, but I will not mention them all as they are not the main causes of delays.
+
+```{r}
+
+```
+
+Figure 2: Distribution of Subway Delay Reasons
+
+Figure 2 illustrates the main reasons for subway delays.
+The main cause of delays for the subway is patron, injury, incident, and mechanical issues.
+Other reasons can be observed in Figure 2, but I will not mention them all as they are not the main causes of delays.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 Other reasons can be observed in Figure 2, but I will not mention them all as they are not the main causes of delays.
+
+```{r}
+
+```
+
+Figure 3:The trend of delays based on the day of the week
+
+Figure 3 shows the trend of delays based on the day of the week.
+We can observe which day experiences the most delays and which day experiences the least.
+It also provides an overview of the delay trend throughout the week.
+
+This information offers valuable insight for the TTC to prepare alternative solutions for delays.
+For instance, they could deploy more buses or trains on days with higher delays compared to days with fewer delays.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
+subtitle: "Insights from Jan 1 to Aug 31"
 author: "Dong Jun Yoon"

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 We can indicate that delays in the bus has occurred approximately 2.35 times more than the subway delay.
-
-Both datasets went through basic cleaning for readability and irrelevant or unusable columns were removed and not considered in this report.
-Originally, the subway data reported the incident causing the delay as a unique code rather than an understandable description.
-This description was included instead in a separate table from the same package (Data 2023b).
-Using merge from dplyr (Wickham et al.
-2023), the incident was mapped to a generalized version of the description to match with the same set of generalized descriptions in the bus delay data.
-This selection into sections based on the description important to note due to the potential subjectivity of the sorting.
-There are incident descriptions in which the record may fall in one or the other.
-Please see the data cleaning scripts for more details.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 The dataset provides information that offers insights of public transit delays across different types of transportation.
-The y-axis represents  The x-axis corresponds ,representing the total income for each year.
 
@@
 ```{r}
+install.packages("kableExtra")
+
+library(kableExtra)
 library(dplyr)
 library(knitr)
+
 data <- read.csv("ttc_bus_delay_data_2024.csv")
@@
 
-# Print the data with lines between columns
-kable(subset_data) 
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
+
 ```
@@
 ```{r}
+library(kableExtra)
 library(dplyr)
 library(knitr)
+
+data <- read.csv("ttc_streetcar_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Incident, Min.Delay, Min.Gap) %>% 
+  head(10)
+
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
+
+```
+Table 2: Sample of streetcar delay statistics; the first 10 rows of TTC subway delay over time: Jan 1 to Aug 31, 2024.
+
+```{r}
+library(kableExtra)
+library(dplyr)
+library(knitr)
+
 data <- read.csv("ttc_subway_delay_data_2024.csv")
@@
 
-# Print the data with lines between columns
-kable(subset_data) 
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
 ```
-Table 2: Sample of subway delay statistics; the first 10 rows of TTC subway delay over time: Jan 1 to Aug 31, 2024.
+Table 3: Sample of subway delay statistics; the first 10 rows of TTC subway delay over time: Jan 1 to Aug 31, 2024.
 
-Both Table 1 and Table 2 include:
+Table 1, Table 2, Table 3 include:
 
@@
 3. Day: The dataset indicates the day of the week when the delay occurred.
-4. Incident: The dataset displays the reason for the delay, such as a general delay, emergency services, or security issues.
+4. Incident: The dataset displays the reason for the delay, such as a general delay, emergency services, or security issues. Incident is displayed in code for Table 3.
 5.
@@
 
-The total bus delay dataset contains 40,447 entries, while the subway delay dataset contains 17,517 entries.
-We can indicate that delays in the bus has occurred approximately 2.35 times more than the subway delay.
+The total bus delay dataset contains 40,447 entries, while the subway delay dataset contains 17,517 entries, and streetcar delay dataset contains 9,932 entries.
+We can indicate that delays in the bus has occurred approximately 2.35 times more than the subway delay and 4.07 times more than the streetcar delay.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 # Introduction
-
 Having operated for over 100 years, the Toronto Transit Commission (TTC) has become one of the most visible and representative public transportation organizations in North America.
@@
 The dataset provides information that offers insights of public transit delays across different types of transportation.
+The y-axis represents  The x-axis corresponds ,representing the total income for each year.
 
@@
 ```{r}
+# Load the required libraries
+library(ggplot2)
+library(dplyr)
+
+# Read the data from both CSV files
+bus_data <- read.csv("ttc_bus_delay_data_2024.csv")
+streetcar_data <- read.csv("ttc_streetcar_delay_data_2024.csv")
+
+# Combine the two data frames into one
+combined_data <- bind_rows(bus_data, streetcar_data)
+
+# Summarize the data by incident type (combining bus and streetcar delays)
+incident_summary <- combined_data %>%
+  group_by(Incident) %>%
+  summarise(Total_Incidents = n()) %>%
+  arrange(desc(Total_Incidents))
+
+# Plot the total incidents for each incident type using ggplot2
+ggplot(incident_summary, aes(x = reorder(Incident, -Total_Incidents), y = Total_Incidents)) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  labs(title = "Reasons of Bus and Streetcar Delay", 
+       x = "Incident Type", 
+       y = "Total Incidents") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better readability
 
 ```
-
 Figure 1: Distribution of Bus and Streetcar Delay Reasons
@@
 ```{r}
+library(ggplot2)
+library(dplyr)
+
+subway_data <- read.csv("Subway_count_2024.csv")
+
+subway_data_clean <- subway_data %>%
+  filter(!is.na(Delay.Group) & !is.na(Count) & Count > 0)
+
+# Summarize the data by Delay.Group
+delay_group_summary <- subway_data_clean %>%
+  group_by(Delay.Group) %>%
+  summarise(Total_Count = sum(Count)) %>%  # Sum up the Count column for each Delay.Group
+  arrange(desc(Total_Count))  # Arrange by total delays in descending order
+
+# Plot the total incidents for each delay group using ggplot2
+ggplot(delay_group_summary, aes(x = reorder(Delay.Group, -Total_Count), y = Total_Count)) +
+  geom_bar(stat = "identity", fill = "tomato") +
+  labs(title = "Total Delays by Delay Group (TTC Subway)", 
+       x = "Delay Group", 
+       y = "Total Delays") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better readability
 
@@
 ```{r}
+# Load necessary libraries
+library(dplyr)
+library(ggplot2)
+library(lubridate)
 
+# Define file paths (replace with actual paths)
+file1 <- ("ttc_subway_delay_data_2024.csv")
+file2 <- ("ttc_bus_delay_data_2024.csv")
+file3 <- ("ttc_streetcar_delay_data_2024.csv")
+
+data1 <- read.csv(file1)
+data2 <- read.csv(file2)
+data3 <- read.csv(file3)
+
+# Inspect column names and structure
+print(names(data1))
+print(names(data2))
+print(names(data3))
+
+# Assuming the date column might be named 'Date'
+data1$date <- as.Date(data1$Date, format = "%Y-%m-%d")
+data2$date <- as.Date(data2$Date, format = "%Y-%m-%d")
+data3$date <- as.Date(data3$Date, format = "%Y-%m-%d")
+
+# Extract the day of the week for each file and count incidents
+day_counts_file1 <- data1 %>%
+  mutate(day_of_week = wday(date, label = TRUE)) %>%
+  group_by(day_of_week) %>%
+  summarise(total_count = n()) %>%
+  mutate(file = "File 1")
+
+day_counts_file2 <- data2 %>%
+  mutate(day_of_week = wday(date, label = TRUE)) %>%
+  group_by(day_of_week) %>%
+  summarise(total_count = n()) %>%
+  mutate(file = "File 2")
+
+day_counts_file3 <- data3 %>%
+  mutate(day_of_week = wday(date, label = TRUE)) %>%
+  group_by(day_of_week) %>%
+  summarise(total_count = n()) %>%
+  mutate(file = "File 3")
+
+# Combine the results into a single dataframe
+combined_day_counts <- bind_rows(day_counts_file1, day_counts_file2, day_counts_file3)
+
+# Plot the variation of delay incidents by day of the week for each file
+ggplot(combined_day_counts, aes(x = day_of_week, y = total_count, color = file, group = file)) +
+  geom_line() +
+  geom_point() +
+  labs(title = "Variation of Delay Incidents by Day of the Week",
+       x = "Day of the Week",
+       y = "Total Count",
+       color = "File") +
+  theme_minimal()
 ```
-
 Figure 3:The trend of delays based on the day of the week

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 # Load necessary libraries
+library(ggplot2)
 library(dplyr)
-library(ggplot2)
-library(lubridate)
 
-# Define file paths (replace with actual paths)
-file1 <- ("ttc_subway_delay_data_2024.csv")
-file2 <- ("ttc_bus_delay_data_2024.csv")
-file3 <- ("ttc_streetcar_delay_data_2024.csv")
+# Load datasets (replace with actual file paths)
+bus_data <- read.csv('ttc_bus_delay_data_2024.csv')
+streetcar_data <- read.csv('ttc_streetcar_delay_data_2024.csv')
+subway_data <- read.csv('ttc_subway_delay_data_2024.csv')
 
-data1 <- read.csv(file1)
-data2 <- read.csv(file2)
-data3 <- read.csv(file3)
+# Create a mapping of full day names to their abbreviations
+day_abbreviations <- c("Monday" = "Mon", "Tuesday" = "Tue", "Wednesday" = "Wed", 
+                       "Thursday" = "Thu", "Friday" = "Fri", "Saturday" = "Sat", 
+                       "Sunday" = "Sun")
 
-# Inspect column names and structure
-print(names(data1))
-print(names(data2))
-print(names(data3))
+# Function to abbreviate day names
+abbreviate_day <- function(day) {
+  return(day_abbreviations[day])
+}
 
-# Assuming the date column might be named 'Date'
-data1$date <- as.Date(data1$Date, format = "%Y-%m-%d")
-data2$date <- as.Date(data2$Date, format = "%Y-%m-%d")
-data3$date <- as.Date(data3$Date, format = "%Y-%m-%d")
+# Group and filter data for each vehicle type, then abbreviate day names
+bus_delays_by_day <- bus_data %>%
+  filter(Day %in% names(day_abbreviations)) %>%
+  group_by(Day) %>%
+  summarise(Count = n()) %>%
+  mutate(Day = abbreviate_day(Day))
 
-# Extract the day of the week for each file and count incidents
-day_counts_file1 <- data1 %>%
-  mutate(day_of_week = wday(date, label = TRUE)) %>%
-  group_by(day_of_week) %>%
-  summarise(total_count = n()) %>%
-  mutate(file = "File 1")
+streetcar_delays_by_day <- streetcar_data %>%
+  filter(Day %in% names(day_abbreviations)) %>%
+  group_by(Day) %>%
+  summarise(Count = n()) %>%
+  mutate(Day = abbreviate_day(Day))
 
-day_counts_file2 <- data2 %>%
-  mutate(day_of_week = wday(date, label = TRUE)) %>%
-  group_by(day_of_week) %>%
-  summarise(total_count = n()) %>%
-  mutate(file = "File 2")
+subway_delays_by_day <- subway_data %>%
+  filter(Day %in% names(day_abbreviations)) %>%
+  group_by(Day) %>%
+  summarise(Count = n()) %>%
+  mutate(Day = abbreviate_day(Day))
 
-day_counts_file3 <- data3 %>%
-  mutate(day_of_week = wday(date, label = TRUE)) %>%
-  group_by(day_of_week) %>%
-  summarise(total_count = n()) %>%
-  mutate(file = "File 3")
+# Combine the data
+bus_delays_by_day$vehicle <- "Bus"
+streetcar_delays_by_day$vehicle <- "Streetcar"
+subway_delays_by_day$vehicle <- "Subway"
 
-# Combine the results into a single dataframe
-combined_day_counts <- bind_rows(day_counts_file1, day_counts_file2, day_counts_file3)
+combined_data <- rbind(bus_delays_by_day, streetcar_delays_by_day, subway_delays_by_day)
 
-# Plot the variation of delay incidents by day of the week for each file
-ggplot(combined_day_counts, aes(x = day_of_week, y = total_count, color = file, group = file)) +
-  geom_line() +
+# Create the plot with abbreviated day labels
+ggplot(combined_data, aes(x = Day, y = Count, color = vehicle, group = vehicle)) +
+  geom_line(size = 1) +
   geom_point() +
-  labs(title = "Variation of Delay Incidents by Day of the Week",
+  labs(title = "Number of delays caused in day, by Vehicle",
        x = "Day of the Week",
-       y = "Total Count",
-       color = "File") +
-  theme_minimal()
+       y = "Count of Delays",
+       color = "Vehicle") +
+  theme_minimal() +
+  scale_x_discrete(limits = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))
 ```

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 subset_data <- data %>%
-  select(Date, Time, Day, Incident, Min.Delay, Min.Gap) %>% 
+  select(Date, Time, Day, Incident, Min_Delay, Min_Gap) %>% 
   head(10)
@@
 subset_data <- data %>%
-  select(Date, Time, Day, Code, Min.Delay, Min.Gap) %>% 
+  select(Date, Time, Day, Code, Min_Delay, Min_Gap) %>% 
   head(10)
@@
 5.
-Min.Delay and Min.Gap: The dataset likely represents 'Min Delay' and 'Min Gap,' both measured in minutes.
+Min_Delay and Min_Gap: The dataset likely represents 'Min Delay' and 'Min Gap,' both measured in minutes.
 'Min Delay' refers to the delay in the schedule for the next bus, while 'Min Gap' indicates the scheduled time, between the bus ahead and the following bus.
@@
 ```
-Figure 3:The trend of delays based on the day of the week
+Figure 3: The trend of delays based on the day of the week
 
@@
 
-This information offers valuable insight for the TTC to prepare alternative solutions for delays.
-For instance, they could deploy more buses or trains on days with higher delays compared to days with fewer delays.
+This information provides valuable insights for the TTC to prepare alternative solutions for delays.
+For instance, they could deploy more buses or trains on days with higher delays compared to those with fewer delays.
+In this case, the TTC could operate more buses on Tuesdays, as an upward trend in delays is observed from Monday to Tuesday.
+Conversely, the TTC could reduce the number of buses on weekends, as there is a downward trend in delays during that time.
+
+```{r}
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Load datasets (replace with actual file paths)
+bus_data <- read.csv('ttc_bus_delay_data_2024.csv')
+streetcar_data <- read.csv('ttc_streetcar_delay_data_2024.csv')
+subway_data <- read.csv('ttc_subway_delay_data_2024.csv')
+
+# Summarize total number of delays and average delay time for each vehicle
+bus_summary <- bus_data %>%
+  summarise(Total_Delays = n(), Avg_Delay_Time = mean(`Min_Delay`, na.rm = TRUE))
+
+streetcar_summary <- streetcar_data %>%
+  summarise(Total_Delays = n(), Avg_Delay_Time = mean(`Min_Delay`, na.rm = TRUE))
+
+subway_summary <- subway_data %>%
+  summarise(Total_Delays = n(), Avg_Delay_Time = mean(`Min_Delay`, na.rm = TRUE))
+
+# Combine the summaries into one data frame
+summary_data <- data.frame(
+  Vehicle = c("Bus", "Streetcar", "Subway"),
+  Total_Delays = c(bus_summary$Total_Delays, streetcar_summary$Total_Delays, subway_summary$Total_Delays),
+  Avg_Delay_Time = c(bus_summary$Avg_Delay_Time, streetcar_summary$Avg_Delay_Time, subway_summary$Avg_Delay_Time)
+)
+
+# Plot 1: Total Number of Delays per Vehicle
+ggplot(summary_data, aes(x = Vehicle, y = Total_Delays, fill = Vehicle)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Total Number of Delays per Vehicle", x = "Vehicle", y = "Total Delays") +
+  theme_minimal()
+
+# Plot 2: Average Delay Time per Vehicle
+ggplot(summary_data, aes(x = Vehicle, y = Avg_Delay_Time, fill = Vehicle)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Average Delay Time per Vehicle (in Minutes)", x = "Vehicle", y = "Average Delay Time (Minutes)") +
+  theme_minimal()
+
+```
+Figure 4: Total delay time and average delay time for each type of vehicles
+
+In Figure 4, we observe the trend of total delay time and average delay time for each type of transportation.
+A closer look at the chart reveals that buses tend to have the highest total delay time and average delay time among all vehicles, with an total delay time of 40,000 minutes and average delay time of approximately 23 minutes which is about 8.8 times longer than the average subway delay time.
+Eventually, the streetcar has the least total delay time among all the vehicles; however, it has a longer average delay time than the subway.
 

### 2024-09-26 paper/paper.qmd
Update paper.qmd

@@
 ```
-
 # Introduction
@@
 Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
-This paper uses the programming language `R`[@citeR] .
-The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].
 
@@
 
-# Data Visualization
+# Data Visualization {#sec-results}
 ```{r}
@@
 
-# Discussion
+# Discussion {#sec-Discussion}
+This paper investigates the correlation of transit delays across different modes of public transportation operated by the Toronto Transit Commission (TTC), namely buses, streetcars, and subways.
+By analyzing datasets from January 1 to August 31, 2024, the paper provides insights into the causes and frequency of delays, for example it illustrates uncover patterns in transit delays, comparing delay causes, trends over time, and variations across different vehicle types.
+This is supported by visualizations showing in the figures above.
 
-Relate your analysis to the themes mentioned in Bouie (2022), discussing the importance of remembering and analyzing historical events through data.
+One key insight from the paper is that buses tend to experience delays more frequently than subways or streetcars, occurring approximately 2.35 times more often than subway delays and 4.07 times more than streetcar delays.
+This is a significant finding, as it suggests that the bus system is less reliable compared to other modes of transportation, likely due to factors such as traffic conditions, mechanical issues, and operational difficulties.Another observation is the difference in the reasons for delays among the different transportation types.
+For buses and streetcars, mechanical and operational issues are the leading causes of delays, while for subways, the main causes are patron-related incidents and mechanical failures.
+This differentiation highlights how the nature of the transportation system influences the kinds of challenges they face, emphasizing the need for tailored solutions to address these issues.
 
-# Model
+A possible weakness is its reliance on limited data from a single year (2024), which may not capture long-term trends or variations in delay patterns over time.
+Additionally, the report only includes data up to August 31, which does not represent a full year.
+Moreover, while the analysis uses statistical and visualization tools effectively, it does not deeply explore underlying causes beyond mechanical or operational issues.
+Another potential limitation is the lack of consideration for external factors like weather conditions, traffic accidents, or city-wide events that might influence transit delays.
+Future research could build upon this analysis by expanding the dataset to include multiple years or integrating external factors, such as traffic patterns, weather conditions, or special events, to provide a more comprehensive understanding of the causes of delays.
+Additionally, more detailed exploration into specific operational or technical issues causing delays for each transportation mode would help the TTC implement targeted solutions.
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
-# Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
-\newpage
+# Conclusion
+In conclusion, this paper highlights key insights into transit delays across the TTC’s buses, streetcars, and subways based on data from January to August 2024.
+The analysis reveals that buses experience delays far more frequently than subways and streetcars, largely due to mechanical and operational issues, while subway delays are often caused by passenger-related incidents.
+Recognizing these patterns could help the TTC address specific repair needs and implement methods to reduce failures, ultimately increasing customer satisfaction and improving transportation for residents in the Toronto area.
 
@@
 Austria: R Foundation for Statistical Computing. https://www.R-project.org/.
+
+Xie, Yihui. 2023. Knitr: A General-Purpose Package for Dynamic Report Generation in r.
+https://yihui.org/knitr/.
+
+Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2024. Readr: Read Rectangular Text Data.
+27. https://readr.tidyverse.org.
+
+Wickham, Hadley. 2016. Ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New
+York. https://ggplot2.tidyverse.org.
+
+Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis Vaughan. 2023. Dplyr: A Grammar of Data Manipulation. https://dplyr.tidyverse.org.

### 2024-09-27 paper/paper.qmd
Update paper.qmd

@@
 date-format: long
-abstract: "This paper analyzes TTC delay data to understand patterns and causes of delays.
-It finds buses experience the most delays, especially on certain routes, while subways have frequent undocumented delays.
-Mechanical issues, operations, and diversions are most common delay causes.
-The analysis indicates the need to reduce bus delays through more vehicles or tactics like bus bridging on certain routes."
+abstract: "This paper provides analyzes of TTC delay data to understand the causes of delays.
+It illustrates uncover patterns in transit delays, comparing delay causes, trends over time, and variations across different vehicle types.
+Buses tend to experience delays more frequently than subways or streetcars, occurring approximately 2.35 times more often than subway delays and 4.07 times more than streetcar delays.
+It suggests that the bus system is less reliable compared to other modes of transportation, likely due to factors such as traffic conditions, mechanical issues, and operational difficulties."
 format: pdf
@@
 bibliography: references.bib
+---
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-library(tidyverse)
-library(palmerpenguins)
-```
 # Introduction
@@
 # Overview of datasets
-```{r}
+```{r, echo=FALSE}
+suppressMessages({
   install.packages("kableExtra")
@@
   library(knitr)
+})
 
@@
   kable_styling(full_width = F, position = "center")
-
 ```
@@
 
-```{r}
+```{r, echo=FALSE}
 library(kableExtra)
@@
 # Data Visualization {#sec-results}
-```{r}
+```{r, echo=FALSE}
 # Load the required libraries
@@
 
-```{r}
+```{r, echo=FALSE}
 library(ggplot2)
@@
 
-```{r}
+```{r, echo=FALSE}
 # Load necessary libraries
@@
 One key insight from the paper is that buses tend to experience delays more frequently than subways or streetcars, occurring approximately 2.35 times more often than subway delays and 4.07 times more than streetcar delays.
-This is a significant finding, as it suggests that the bus system is less reliable compared to other modes of transportation, likely due to factors such as traffic conditions, mechanical issues, and operational difficulties.Another observation is the difference in the reasons for delays among the different transportation types.
+This is a significant finding, as it suggests that the bus system is less reliable compared to other modes of transportation, likely due to factors such as traffic conditions, mechanical issues, and operational difficulties.
+Another observation is the difference in the reasons for delays among the different transportation types.
 For buses and streetcars, mechanical and operational issues are the leading causes of delays, while for subways, the main causes are patron-related incidents and mechanical failures.

### 2024-09-27 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,19 +1,158 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates Code
+# Author: Dong Jun Yoon
+# Date: 26 September 2024 
+# Contact: dongjun.yoon@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(kableExtra)
+library(dplyr)
+library(knitr)
+library(ggplot2)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+# data <- read.csv("ttc_bus_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Incident, Min_Delay, Min_Gap) %>% 
+  head(10)
+
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
+
+#data <- read.csv("ttc_streetcar_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Incident, Min_Delay, Min_Gap) %>% 
+  head(10)
+
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
+
+#data <- read.csv("ttc_subway_delay_data_2024.csv")
+
+subset_data <- data %>%
+  select(Date, Time, Day, Code, Min_Delay, Min_Gap) %>% 
+  head(10)
+
+kable(subset_data, format = "pipe", align = 'l') %>%
+  kable_styling(full_width = F, position = "center")
+
+#bus_data <- read.csv("ttc_bus_delay_data_2024.csv")
+streetcar_data <- read.csv("ttc_streetcar_delay_data_2024.csv")
+
+combined_data <- bind_rows(bus_data, streetcar_data)
+
+incident_summary <- combined_data %>%
+  group_by(Incident) %>%
+  summarise(Total_Incidents = n()) %>%
+  arrange(desc(Total_Incidents))
[…]

### 2024-09-27 scripts/01-download_data.R
Update 01-download_data.R

@@ -1,12 +1,9 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data
+# Author: Dong Jun Yoon
+# Date: 26 September 2024 
+# Contact: dongjun.yoon@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(opendatatoronto)

### 2024-09-27 scripts/03-test_data.R
Update 03-test_data.R

@@ -1,12 +1,9 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the code
+# Author: Dong Jun Yoon
+# Date: 26 September 2024 
+# Contact: dongjun.yoon@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-27 scripts/04-model.R
Update 04-model.R

@@ -1,12 +1,9 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models
+# Author: Dong Jun Yoon
+# Date: 26 September 2024 
+# Contact: dongjun.yoon@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-27 scripts/05-replications.R
Update 05-replications.R

@@ -1,19 +1,16 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Replicated graphs from
+# Author: Dong Jun Yoon
+# Date: 26 September 2024 
+# Contact: dongjun.yoon@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Load data ####
-# [...ADD CODE HERE...]
+
 
 
 

### 2024-09-27 scripts/01-download_data.R
Update 01-download_data.R

@@ -6,17 +6,18 @@
 # License: MIT
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+library(kableExtra)
+library(dplyr)
+library(knitr)
+library(ggplot2)
+
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
 
 
 
 #### Save data ####
-# [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 

### 2024-09-27 scripts/03-test_data.R
Update 03-test_data.R

@@ -7,6 +7,10 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(kableExtra)
+library(dplyr)
+library(knitr)
+library(ggplot2)
+
 
 #### Test data ####

### 2024-09-27 scripts/04-model.R
Update 04-model.R

@@ -8,6 +8,10 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(kableExtra)
+library(dplyr)
+library(knitr)
+library(ggplot2)
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")

### 2024-09-27 scripts/05-replications.R
Update 05-replications.R

@@ -7,7 +7,10 @@
 
 #### Workspace setup ####
 library(tidyverse)
-
+library(kableExtra)
+library(dplyr)
+library(knitr)
+library(ggplot2)
 
 #### Load data ####
 
